### 2025-01-15 BAI/exercises.tex
Added current state.
Added some lecture questions.

\section[2024]{Mock exam}

@@

\section[2023]{1st exam}

@@

\section[2022]{1st exam}

\begin{exercise}{Multiple Choice}
  \begin{enumerate}
    \item In which models is backpropagation used for learning?

      \begin{itemize}
        \item Multilayer perceptron (MLP)
        \item Convolutional neural network (CNN)
        \item Self-organizing map (SOM)
        \item None of the above
      \end{itemize}

    \item What does "embodied" mean for language?

      \begin{itemize}
        \item Language is based on the physical world.
        \item Language is based on the ground truth.
        \item Language is based on the ground state.
        \item Language is based on the ground floor.
      \end{itemize}

    \item What are the two streams and their tasks in human vision?

      \begin{itemize}
        \item Dorsal stream for spatial vision and ventral stream for object recognition
        \item Ventral stream for spatial vision and dorsal stream for object recognition
        \item Dorsal stream for object recognition and ventral stream for spatial vision
        \item Ventral stream for object recognition and dorsal stream for spatial vision
      \end{itemize}
  \end{enumerate}

>>>>

\sheet{Lecture Questions}
\begin{exercise}{Spiking Neural Networks}
  \begin{enumerate}
    \item Explain the concept of spiking neural networks and how they resemble biological information transmission.
    \item What is the difference between temporal coding and static learning?
    \item How is learning in spiking neural networks based on synaptic correlations?
    \item What is Spike-Timing Dependent Plasticity?
    \item Differentiate rate-coded, integrate-and-fire, and spike-response models.
  \end{enumerate}

  \begin{solution}
    \begin{enumerate}
      \item Spiking neural networks are a type of artificial neural network that model the behavior of biological neurons. They use spikes, or action potentials, to transmit information between neurons, similar to how biological neurons communicate.
      \item Temporal coding is a method of encoding information in the timing of spikes, while static learning is a method of encoding information in the strength of synaptic connections.
      \item Learning in spiking neural networks is based on synaptic correlations, which are the correlations between the timing of pre- and post-synaptic spikes.
      \item Spike-Timing Dependent Plasticity is a learning rule that strengthens or weakens synaptic connections based on the timing of pre- and post-synaptic spikes.
      \item Rate-coded models use firing rates to encode information, integrate-and-fire models use membrane potentials to encode information, and spike-response models use spike times to encode information.
    \end{enumerate}
  \end{solution}
\end{exercise}

\sheet[2024]{Mock exam}

@@

\sheet[2023]{1st exam}

@@

\sheet[2022]{1st exam}

\begin{exercise}{Multiple Choice}
  \begin{enumerate}
    \item In which models is backpropagation used for learning?
      \begin{itemize}
        \item Multilayer perceptron (MLP)
        \item Convolutional neural network (CNN)
        \item Self-organizing map (SOM)
        \item None of the above
      \end{itemize}

    \item What does "embodied" mean for language?
      \begin{itemize}
        \item Language is based on the physical world.
        \item Language is based on the ground truth.
        \item Language is based on the ground state.
        \item Language is based on the ground floor.
      \end{itemize}

    \item What are the two streams and their tasks in human vision?
      \begin{itemize}
        \item Dorsal stream for spatial vision and ventral stream for object recognition
        \item Ventral stream for spatial vision and dorsal stream for object recognition
        \item Dorsal stream for object recognition and ventral stream for spatial vision
        \item Ventral stream for object recognition and dorsal stream for spatial vision
      \end{itemize}
  \end{enumerate}
